Untitled

### 2018-07-31 PaperCode.Rmd
Get back MSOA model
I made an MSOA model that worked really well. Sadly I crashed the computer and lost all the code. The re-written code produces a rubbish model, I don't know why. Maybe turning it off and on will help...

#Saleries
```{r}

@@

    tibble(v1 =predict(BootMod[[.x]], ModData[testvect,], type = "response")>0.5) 
  }) %>%
  bind_cols() %>% set_names(make.names(1:length(BootMod)))# %>%
 # mutate(BootResult =rowSums(.)/ncol(.)>0.5)

>>>>

#Saleries

Problem here with the MSOA/LSOA code in the IncomeEst

@@

    tibble(v1 =predict(BootMod[[.x]], ModData[testvect,], type = "response")>0.5) 
  }) %>%
  bind_cols() %>% set_names(make.names(1:length(BootMod)))
